---
title: "MLB Results By Pitch Type and Count"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gridExtra)

```

# Count: 0-0

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_00_woba.rds"),
             readRDS("fastball_00_swing.rds"),
             readRDS("fastball_00_whiff.rds"),
             readRDS("breaking_00_woba.rds"),
             readRDS("breaking_00_swing.rds"),
             readRDS("breaking_00_whiff.rds"),
             readRDS("offspeed_00_woba.rds"),
             readRDS("offspeed_00_swing.rds"),
             readRDS("offspeed_00_whiff.rds"),
             ncol = 3,
             nrow = 3)
```

# Count: 0-1

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_01_woba.rds"),
             readRDS("fastball_01_swing.rds"),
             readRDS("fastball_01_whiff.rds"),
             readRDS("breaking_01_woba.rds"),
             readRDS("breaking_01_swing.rds"),
             readRDS("breaking_01_whiff.rds"),
             readRDS("offspeed_01_woba.rds"),
             readRDS("offspeed_01_swing.rds"),
             readRDS("offspeed_01_whiff.rds"),
             ncol = 3,
             nrow = 3)
```

# Count: 0-2

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_02_woba.rds"),
             readRDS("fastball_02_swing.rds"),
             readRDS("fastball_02_whiff.rds"),
             readRDS("breaking_02_woba.rds"),
             readRDS("breaking_02_swing.rds"),
             readRDS("breaking_02_whiff.rds"),
             readRDS("offspeed_02_woba.rds"),
             readRDS("offspeed_02_swing.rds"),
             readRDS("offspeed_02_whiff.rds"),
             ncol = 3,
             nrow = 3)
```

# Count: 1-0

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_10_woba.rds"),
             readRDS("fastball_10_swing.rds"),
             readRDS("fastball_10_whiff.rds"),
             readRDS("breaking_10_woba.rds"),
             readRDS("breaking_10_swing.rds"),
             readRDS("breaking_10_whiff.rds"),
             readRDS("offspeed_10_woba.rds"),
             readRDS("offspeed_10_swing.rds"),
             readRDS("offspeed_10_whiff.rds"),
             ncol = 3,
             nrow = 3)
```

# Count: 1-1

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_11_woba.rds"),
             readRDS("fastball_11_swing.rds"),
             readRDS("fastball_11_whiff.rds"),
             readRDS("breaking_11_woba.rds"),
             readRDS("breaking_11_swing.rds"),
             readRDS("breaking_11_whiff.rds"),
             readRDS("offspeed_11_woba.rds"),
             readRDS("offspeed_11_swing.rds"),
             readRDS("offspeed_11_whiff.rds"),
             ncol = 3,
             nrow = 3)
```

# Count: 1-2

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_12_woba.rds"),
             readRDS("fastball_12_swing.rds"),
             readRDS("fastball_12_whiff.rds"),
             readRDS("breaking_12_woba.rds"),
             readRDS("breaking_12_swing.rds"),
             readRDS("breaking_12_whiff.rds"),
             readRDS("offspeed_12_woba.rds"),
             readRDS("offspeed_12_swing.rds"),
             readRDS("offspeed_12_whiff.rds"),
             ncol = 3,
             nrow = 3)
```

# Count: 2-0

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_20_woba.rds"),
             readRDS("fastball_20_swing.rds"),
             readRDS("fastball_20_whiff.rds"),
             readRDS("breaking_20_woba.rds"),
             readRDS("breaking_20_swing.rds"),
             readRDS("breaking_20_whiff.rds"),
             readRDS("offspeed_20_woba.rds"),
             readRDS("offspeed_20_swing.rds"),
             readRDS("offspeed_20_whiff.rds"),
             ncol = 3,
             nrow = 3)
```

# Count: 2-1

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_21_woba.rds"),
             readRDS("fastball_21_swing.rds"),
             readRDS("fastball_21_whiff.rds"),
             readRDS("breaking_21_woba.rds"),
             readRDS("breaking_21_swing.rds"),
             readRDS("breaking_21_whiff.rds"),
             readRDS("offspeed_21_woba.rds"),
             readRDS("offspeed_21_swing.rds"),
             readRDS("offspeed_21_whiff.rds"),
             ncol = 3,
             nrow = 3)
```

# Count: 2-2

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_22_woba.rds"),
             readRDS("fastball_22_swing.rds"),
             readRDS("fastball_22_whiff.rds"),
             readRDS("breaking_22_woba.rds"),
             readRDS("breaking_22_swing.rds"),
             readRDS("breaking_22_whiff.rds"),
             readRDS("offspeed_22_woba.rds"),
             readRDS("offspeed_22_swing.rds"),
             readRDS("offspeed_22_whiff.rds"),
             ncol = 3,
             nrow = 3)
```

# Count: 3-0

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_30_woba.rds"),
             readRDS("fastball_30_swing.rds"),
             readRDS("fastball_30_whiff.rds"),
             readRDS("breaking_30_swing.rds"),
             readRDS("breaking_30_whiff.rds"),
             readRDS("offspeed_30_swing.rds"),
             readRDS("offspeed_30_whiff.rds"),
             ncol = 3,
             nrow = 3, layout_matrix = matrix(c(1,NA,NA,2,4,6,3,5,7), nrow = 3))
```

# Count: 3-1

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_31_woba.rds"),
             readRDS("fastball_31_swing.rds"),
             readRDS("fastball_31_whiff.rds"),
             readRDS("breaking_31_woba.rds"),
             readRDS("breaking_31_swing.rds"),
             readRDS("breaking_31_whiff.rds"),
             readRDS("offspeed_31_woba.rds"),
             readRDS("offspeed_31_swing.rds"),
             readRDS("offspeed_31_whiff.rds"),
             ncol = 3,
             nrow = 3)
```

# Count: 3-2

```{r echo=FALSE, warning = FALSE, fig.width = 10}
grid.arrange(readRDS("fastball_32_woba.rds"),
             readRDS("fastball_32_swing.rds"),
             readRDS("fastball_32_whiff.rds"),
             readRDS("breaking_32_woba.rds"),
             readRDS("breaking_32_swing.rds"),
             readRDS("breaking_32_whiff.rds"),
             readRDS("offspeed_32_woba.rds"),
             readRDS("offspeed_32_swing.rds"),
             readRDS("offspeed_32_whiff.rds"),
             ncol = 3,
             nrow = 3)
```

# Correlations By Pitch Type: FF

### RHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("FF_R_Velocity.rds"),
             readRDS("FF_R_Move_x.rds"),
             readRDS("FF_R_Move_z.rds"),
             readRDS("FF_R_Spin_Rate.rds"),
             readRDS("FF_R_BU.rds"),
             readRDS("FF_R_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

### LHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("FF_L_Velocity.rds"),
             readRDS("FF_L_Move_x.rds"),
             readRDS("FF_L_Move_z.rds"),
             readRDS("FF_L_Spin_Rate.rds"),
             readRDS("FF_L_BU.rds"),
             readRDS("FF_L_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

# Correlations By Pitch Type: FT

### RHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("FT_R_Velocity.rds"),
             readRDS("FT_R_Move_x.rds"),
             readRDS("FT_R_Move_z.rds"),
             readRDS("FT_R_Spin_Rate.rds"),
             readRDS("FT_R_BU.rds"),
             readRDS("FT_R_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

### LHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("FT_L_Velocity.rds"),
             readRDS("FT_L_Move_x.rds"),
             readRDS("FT_L_Move_z.rds"),
             readRDS("FT_L_Spin_Rate.rds"),
             readRDS("FT_L_BU.rds"),
             readRDS("FT_L_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

# Correlations By Pitch Type: FC

### RHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("FC_R_Velocity.rds"),
             readRDS("FC_R_Move_x.rds"),
             readRDS("FC_R_Move_z.rds"),
             readRDS("FC_R_Spin_Rate.rds"),
             readRDS("FC_R_BU.rds"),
             readRDS("FC_R_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

### LHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("FC_L_Velocity.rds"),
             readRDS("FC_L_Move_x.rds"),
             readRDS("FC_L_Move_z.rds"),
             readRDS("FC_L_Spin_Rate.rds"),
             readRDS("FC_L_BU.rds"),
             readRDS("FC_L_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

# Correlations By Pitch Type: SI

### RHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("SI_R_Velocity.rds"),
             readRDS("SI_R_Move_x.rds"),
             readRDS("SI_R_Move_z.rds"),
             readRDS("SI_R_Spin_Rate.rds"),
             readRDS("SI_R_BU.rds"),
             readRDS("SI_R_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

### LHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("SI_L_Velocity.rds"),
             readRDS("SI_L_Move_x.rds"),
             readRDS("SI_L_Move_z.rds"),
             readRDS("SI_L_Spin_Rate.rds"),
             readRDS("SI_L_BU.rds"),
             readRDS("SI_L_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

# Correlations By Pitch Type: SL

### RHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("SL_R_Velocity.rds"),
             readRDS("SL_R_Move_x.rds"),
             readRDS("SL_R_Move_z.rds"),
             readRDS("SL_R_Spin_Rate.rds"),
             readRDS("SL_R_BU.rds"),
             readRDS("SL_R_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

### LHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("SL_L_Velocity.rds"),
             readRDS("SL_L_Move_x.rds"),
             readRDS("SL_L_Move_z.rds"),
             readRDS("SL_L_Spin_Rate.rds"),
             readRDS("SL_L_BU.rds"),
             readRDS("SL_L_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

# Correlations By Pitch Type: CU

### RHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("CU_R_Velocity.rds"),
             readRDS("CU_R_Move_x.rds"),
             readRDS("CU_R_Move_z.rds"),
             readRDS("CU_R_Spin_Rate.rds"),
             readRDS("CU_R_BU.rds"),
             readRDS("CU_R_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

### LHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("CU_L_Velocity.rds"),
             readRDS("CU_L_Move_x.rds"),
             readRDS("CU_L_Move_z.rds"),
             readRDS("CU_L_Spin_Rate.rds"),
             readRDS("CU_L_BU.rds"),
             readRDS("CU_L_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

# Correlations By Pitch Type: KC

### RHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("KC_R_Velocity.rds"),
             readRDS("KC_R_Move_x.rds"),
             readRDS("KC_R_Move_z.rds"),
             readRDS("KC_R_Spin_Rate.rds"),
             readRDS("KC_R_BU.rds"),
             readRDS("KC_R_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

### LHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("KC_L_Velocity.rds"),
             readRDS("KC_L_Move_x.rds"),
             readRDS("KC_L_Move_z.rds"),
             readRDS("KC_L_Spin_Rate.rds"),
             readRDS("KC_L_BU.rds"),
             readRDS("KC_L_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

# Correlations By Pitch Type: CH

### RHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("CH_R_Velocity.rds"),
             readRDS("CH_R_Move_x.rds"),
             readRDS("CH_R_Move_z.rds"),
             readRDS("CH_R_Spin_Rate.rds"),
             readRDS("CH_R_BU.rds"),
             readRDS("CH_R_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

### LHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("CH_L_Velocity.rds"),
             readRDS("CH_L_Move_x.rds"),
             readRDS("CH_L_Move_z.rds"),
             readRDS("CH_L_Spin_Rate.rds"),
             readRDS("CH_L_BU.rds"),
             readRDS("CH_L_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

# Correlations By Pitch Type: FS

### RHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("FS_R_Velocity.rds"),
             readRDS("FS_R_Move_x.rds"),
             readRDS("FS_R_Move_z.rds"),
             readRDS("FS_R_Spin_Rate.rds"),
             readRDS("FS_R_BU.rds"),
             readRDS("FS_R_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```

### LHP
```{r echo=FALSE, warning = FALSE, fig.width = 10, message = FALSE}
grid.arrange(readRDS("FS_L_Velocity.rds"),
             readRDS("FS_L_Move_x.rds"),
             readRDS("FS_L_Move_z.rds"),
             readRDS("FS_L_Spin_Rate.rds"),
             readRDS("FS_L_BU.rds"),
             readRDS("FS_L_Move_Angle.rds"),
             ncol = 3,
             nrow = 2)
```